Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex

\begin{rmk}
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
\end{rmk}

@@

\begin{prp}\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
\left( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \right)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as a commutative factorization pair.
\end{prp}

@@

\brian{define $\PP_0$ factorization algebra}

The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.

>>>>

@@

\begin{prp}
\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
\left( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \right)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as a commutative factorization pair.
\end{prp}

@@

The associated graded factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ are equipped with Poisson brackets that are compatible with the factorization structure.

For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$-algebra. 
Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$-algebra structure.

Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$-algebras.

In light of this, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.

\begin{lmm}
\label{lmm:pois1}
Consider the factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ on a manifold $M$.
Then
\begin{itemize}
\item ${\rm Gr} \; \bU_n (\fg)$ is equipped with the structure of a $\PP_0$-factorization algebra.
\item ${\rm Gr} \; \bZ_n(\fg)$ is equipped with the structure of a $\PP_1$-factorization algebra.
\end{itemize}
\end{lmm}

The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
At the level of the associated graded algebras, we obtain an algebra over a certain classical limit of this operad which takes into account the aforementioned Poisson structures.

The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in \cite{SafronovCoiso}. 
A $\PP_{[n+1,n]}$-algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$-algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.

The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
Together with Lemma \ref{lmm:pois1}, we obtain Proposition \ref{prp:poisson}.

\begin{rmk}
One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$-algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$-algebra $B$. 
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the $\PP_n$-center of the $\PP_n$-{\em enveloping algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
\end{rmk}
